The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-11-29 manuscript/manuscript.qmd
Add interpretation on environmental issue area after education

>>>>

Additionally, the INGOs that survived the registration thresholds are those already "censored" to be relatively safe and non-contentious. This can help explain why some seemingly more contentious issue areas, e.g., environmental INGOs enjoy relatively more operational space. According to [@Plantan:2022], Chinese authorities can see the work of environmental INGOs as providing benefits such as political stability and "selectively ncourage low risk groups and selectively channel higher risk groups into permitted areas". We will further this discussion with the case analysis of two environmental INGOs later.
